outline!

### 2016-05-15 paper.tex

why ceph and corfu?

Short description of CORFU system~\cite{balakrishnan:nsdi12}. It's a log!
While CORFU relies on custom interfaces built into flash devices, an
implementation in Ceph relies upon custom device interfaces to enforce its
protocol.

The state-machine shown in Figure~\ref{fig:corfu-sm} shows the composition of
actions for each component of the CORFU interface. For example, each
operations begins with an \emph{epoch guard}, and a \emph{write} operation
will consult an index and perform a bulk I/O operation.  The primary concern
when mapping an interface onto Ceph is deciding how each native interface is
used in the interface composition.

>>>>

\paragraph*{Programmable Storage and CORFU}
Two aspects of CORFU make its design attractive in the context of
the Ceph storage system. First, CORFU assumes a cluster of flash devices
because log-centric systems tend to have a larger percentage of random reads
making it difficult to achieve high-performance with spinning disks. However,
the speed of the underlying storage does not affect correctness. Thus, in a
software-defined storage system such as Ceph a single implementation can
transparently take advantage of any software or hardware upgrades, and make
use of data management features such as tiering in RADOS, allowing users to
freely choose between media types such as SSD, spinning disks, or emerging
NVRAM technologies.

The second property of CORFU relevant in the context of Ceph is the dependency
CORFU places on the storage device interface.  As was previously discussed, in
order to enforce constraints defined within the CORFU protocol, storage
devices are expected to expose a domain-specific interface specially designed
for the protocol. While the authors of the CORFU paper describe both a
host-based and FPGA-based solution, RADOS directly supports the concept of
custom storage interfaces to its objects that can be used to achieve the
transactional semantics necessary to implement the CORFU storage interfaces.
This feature is called RADOS object classes, and is one of the most powerful
features offered by RADOS for designing storage applications.

\paragraph*{A CORFU Object Interface}
The state-machine shown in Figure~\ref{fig:corfu-sm} shows the composition of
actions for each component of the CORFU interface. For example, each
operations begins with an \emph{epoch guard}, and a \emph{write} operation
will consult an index and perform a bulk I/O operation.  The primary concern
when mapping an interface onto Ceph is deciding how each native interface is
used in the interface composition.
